---
title: "audio processing"
output: html_document
---

```{r}
read_rttm <- function(x,
                      from = NULL,
                      to = NULL) {
  if (length(readLines(x)) > 0) {
    res <- read.table(x, header = FALSE)
    colnames(res)[c(4, 5, 8)] <- c("start", "duration", "tier")
    res$end <- res$start + res$duration
  } else {
    res <- matrix(0, nrow = 0, ncol = 10)
    # res[1, ] <- NA
    colnames(res) <- paste0("V", 1:ncol(res))
    colnames(res)[c(4, 5, 8, 10)] <- c("start", "duration", "tier", "end")
    res <- data.frame(res)
  }

  if (!is.null(from)) {
    res <- res[res$end > from, ]
    if (nrow(res) > 0) {
      if (res$start[1] < from) {
        res$start[1] <- from
        res$duration[1] <- res$end[1] - res$start[1]
      }
    }
  }

  if (!is.null(to)) {
    res <- res[res$start < to, ]
    if (nrow(res) > 0) {
      if (res$end[nrow(res)] > to) {
        res$end[nrow(res)] <- to
        res$duration[nrow(res)] <- res$end[nrow(res)] - res$start[nrow(res)]
      }
    }
  }


  attributes(res)$filename <- basename(x)
  rownames(res) <- NULL
  res
}
```

```{r}
library(tidyverse)
library(ggthemes)
library(ggpubr)
library(readxl)
library(tidyboot)
library(lme4)
library(lubridate)
```

# Read data

```{r}
files <- list.files(path = "../Data/Rttm_Data",pattern = "all.rttm", recursive = TRUE)%>%
  str_subset(pattern = c("00000_00000020201016142243_0001A/all.rttm","191016_1319/all.rttm"), negate = T)

raw_data <- data_frame()
for (f in files) {
  jd <- read_rttm(paste("../Data/Rttm_Data/",f,sep=""))
  source <- str_sub(f,-14,-10)
  id <- str_sub(f,14,19)
  data <- jd %>% mutate(id = id, source = source)
  raw_data <- bind_rows(raw_data, data)
}

write_csv(raw_data, "../Data/merged_data/audio_video_comparison.csv")

raw_data <- read_csv("../Data/merged_data/audio_video_comparison.csv")%>%
  mutate(frequency = "144kHz",
         id = factor(id))
```

# Visualize by tier and source

```{r}
raw_data%>%
  filter(id =="252957")%>%
ggplot(., aes(x = tier, ymin = start, ymax = end, col = source))+
  geom_linerange(position = position_dodge(width = 0.9), size = 4)+
  coord_flip()+
  #geom_segment(aes(x = start, y = tier, xend = end, yend = tier), size = 5, position = posi)+
  theme_minimal()+
  #facet_grid(id~.)+
  #ylim(0,100)+
  scale_color_ptol()

ggsave("./plots/audio_video_comparison_single.png", width = 10, height = 6, scale = 0.75)
```

# Compare performance 
```{r}
comp_data <- raw_data %>%
  group_by(source, id)%>%
  summarise(length = max(end))%>%
  group_by(id)%>%
  summarise(length = min(length))%>%
  right_join(raw_data)%>%
  group_by(id)%>%
  filter(end < length)


unique(raw_data$id)
```

## Correlation
```{r}
p_comp_data <- comp_data %>%
  group_by(id,source,tier)%>%
  summarise(count = n(),
            dur = sum(duration))%>%
  gather(type, value, -id, -source, -tier)%>%
  spread(source, value)

 
ggplot(p_comp_data, aes(x = Audio, y = Video))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(alpha = .5)+
  facet_wrap(type ~ tier, scales = "free",nrow = 2)+
  stat_cor(method = "pearson",  aes(x = Audio, y = Video, label = paste(..rr.label..)), inherit.aes = F, size = 3)+
  ggtitle("144kHZ")+
  theme_minimal()+
  theme(aspect.ratio = 1)
  

ggsave("./plots/audio_video_correlation.png", width = 12, height = 4, scale = 1)
```

## Absolute difference

```{r}
p_comp_data_abs <- comp_data %>%
  group_by(id,source,tier)%>%
  summarise(count = n(),
            duration = sum(duration))%>%
  gather(type, value, -id, -source, -tier)%>%
  spread(source, value)%>%
  mutate(diff = Audio - Video)

 
ggplot(p_comp_data_abs, aes(x = id, y = diff, col = tier))+
  geom_segment(aes(x = id, y = 0, xend = id, yend = diff), alpha = .5, col = "black")+
  geom_hline(yintercept = 0, lty = 2, alpha = .5)+
  geom_point(alpha = .5)+
  ylab("Audio - Video")+
  ggtitle("144kHZ")+
  #geom_histogram(stat = "identity",alpha = .5)+
  facet_grid(tier ~type )+
  theme_minimal()+
  guides(x =  guide_axis(angle = 90))+
  scale_color_ptol()
  

ggsave("./plots/audio_video_diff.png", width = 5, height = 6, scale = 1)
```

# Hand checked data

## Export hand check data for CHI tier

```{r}
library(writexl)

raw_data %>%
  filter(tier == "CHI")%>%
  mutate(check = "",
         comment = "")%>%
  select(id, source, tier, start,check, comment)%>%
  group_by(source,id) %>%
  group_walk(~ write_xlsx(.x, paste0("../Data/merged_data/hand_check/",.y$id,"_",.y$source, ".xlsx")))

```

## Evaluate hand-checked data

```{r}
files <- list.files(path = "../Data/hand_check/",pattern = "*.xlsx", recursive = TRUE)

raw_data <- data_frame()
for (f in files) {
  jd <- read_xlsx(paste("../Data/hand_check/",f,sep=""))
  id <- str_sub(f,0,6)
  source <- str_sub(f,-10,-6)
  data <- jd %>% mutate(id = id, source = source)
  raw_data <- bind_rows(raw_data, data)
}


check_data <- raw_data %>%
  filter(id != "260584")

model <- glmer(check ~ source + (1|id),
      data = check_data, 
      family = binomial)

summary(model)

drop1(model, test = "Chisq")

p1 <- check_data %>%
  group_by(id, source)%>%
  summarise(mean = mean(check))


p2 <- p1 %>%
  group_by(source)%>%
  tidyboot_mean(column = mean)

ggplot()+
  geom_line(data = p1, aes(x = source, y = mean, group = id), alpha = .3)+
  geom_point(data = p1, aes(x = source, y = mean, col = source), alpha = .5)+
  geom_pointrange(data = p2, aes(x = source, y = mean, col = source, ymin = ci_lower, ymax = ci_upper), pch = 5, size = 1, stroke = 2)+
  labs(y = "Proportion match")+
  scale_color_ptol()+
  theme_minimal()
```
# Re-sampled data

## compare 16kHz to 144kHz
```{r}
files <- list.files(path = "../Data/Resampled_Rttm",pattern = "all.rttm", recursive = TRUE)

raw_data_16khz <- data_frame()
for (f in files) {
  jd <- read_rttm(paste("../Data/Resampled_Rttm/",f,sep=""))
  source <- str_sub(f,-14,-10)
  id <- str_sub(f,14,19)
  data <- jd %>% mutate(id = id, source = source)
  raw_data_16khz <- bind_rows(raw_data_16khz, data)
}

write_csv(raw_data_16khz, "../Data/merged_data/audio_video_comparison_resampled.csv")

raw_data_16khz <- read_csv("../Data/merged_data/audio_video_comparison_resampled.csv")%>%
  mutate(frequency = "16kHz")%>%
  mutate(id = factor(id))
```

```{r}
comp_data_samp <- bind_rows(
  raw_data_16khz,
  raw_data
)

p_comp_data_samp <- comp_data_samp %>%
  group_by(id,source, frequency, tier)%>%
  summarise(count = n(),
            duration = sum(duration))%>%
  gather(type, value, -id, -source,-frequency, -tier)%>%
  spread(frequency, value)%>%
  mutate(diff = `144kHz` - `16kHz`)

 
ggplot(p_comp_data_samp, aes(x = `144kHz`, y = `16kHz`, col = source))+
  geom_point(alpha = .5)+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  labs(x = "144kHz" ,y = "16kHz")+
  stat_cor(method = "pearson", aes(x = `144kHz`, y = `16kHz`), inherit.aes = F)+
  #geom_histogram(stat = "identity",alpha = .5)+
  facet_grid(type ~tier)+
  theme_minimal()+
  scale_color_ptol()+
  coord_fixed()

ggsave("./plots/freq_diff.png", width = 12, height = 6, scale = 1.2)
```

## compare audio and video with 144 kHz

```{r}
comp_data <- raw_data_16khz %>%
  group_by(source, id)%>%
  summarise(length = max(end))%>%
  group_by(id)%>%
  summarise(length = min(length))%>%
  right_join(raw_data_16khz)%>%
  group_by(id)%>%
  filter(end < length)

```

### Correlation
```{r}
p_comp_data <- comp_data %>%
  group_by(id,source,tier)%>%
  summarise(count = n(),
            dur = sum(duration))%>%
  gather(type, value, -id, -source, -tier)%>%
  spread(source, value)

 
ggplot(p_comp_data, aes(x = Audio, y = Video))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(alpha = .5)+
  facet_wrap(type ~ tier, scales = "free",nrow = 2)+
  stat_cor(method = "pearson",  aes(x = Audio, y = Video, label = paste(..rr.label..)), inherit.aes = F, size = 3)+
  ggtitle("16kHZ")+
  theme_minimal()+
  theme(aspect.ratio = 1)
  

ggsave("./plots/audio_video_correlation_16kHz.png", width = 12, height = 4, scale = 1)
```

## Absolute difference

```{r}
p_comp_data_abs <- comp_data %>%
  group_by(id,source,tier)%>%
  summarise(count = n(),
            duration = sum(duration))%>%
  gather(type, value, -id, -source, -tier)%>%
  spread(source, value)%>%
  mutate(diff = Audio - Video)

 
ggplot(p_comp_data_abs, aes(x = id, y = diff, col = tier))+
  geom_segment(aes(x = id, y = 0, xend = id, yend = diff), alpha = .5, col = "black")+
  geom_hline(yintercept = 0, lty = 2, alpha = .5)+
  geom_point(alpha = .5)+
  ylab("Audio - Video")+
  ggtitle("16kHZ")+
  facet_grid(tier ~type )+
  theme_minimal()+
  guides(x =  guide_axis(angle = 90))+
  scale_color_ptol()
  

ggsave("./plots/audio_video_diff_16kHz.png", width = 5, height = 6, scale = 1)
```

# Re-run model

```{r}
files <- list.files(path = "../Data/Orig_Rttm",pattern = "all.rttm", recursive = TRUE)%>%
  str_subset(pattern = c("00000_00000020201016142243_0001A/all.rttm","191016_1319/all.rttm"), negate = T)

raw_data_run2 <- data_frame()
for (f in files) {
  jd <- read_rttm(paste("../Data/Orig_Rttm/",f,sep=""))
  source <- str_sub(f,-14,-10)
  id <- str_sub(f,14,19)
  data <- jd %>% mutate(id = id, source = source)
  raw_data_run2 <- bind_rows(raw_data_run2, data)
}

write_csv(raw_data_run2, "../Data/merged_data/audio_video_comparison_run2.csv")

raw_data_run2 <- read_csv("../Data/merged_data/audio_video_comparison_run2.csv")%>%
  mutate(run = "run2",
         id = factor(id))
```

## compare 2 model runs

```{r}
comp_data_run <- bind_rows(
  raw_data %>% mutate(run = "run1"),
  raw_data_run2
)

raw_data

```

### Correlation
```{r}
p_comp_data_run <- comp_data_run %>%
  group_by(id,source,tier,run)%>%
  summarise(count = n(),
            dur = sum(duration))%>%
  gather(type, value, -id, -source, -tier, -run)%>%
  spread(run, value)

 
ggplot(p_comp_data_run, aes(x = run1, y = run2))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(alpha = .5)+
  facet_wrap(source + type ~ tier, scales = "free",nrow = 2)+
  stat_cor(method = "pearson",  aes(x = run1, y = run2))+
  theme_minimal()+
  theme(aspect.ratio = 1)
  

ggsave("./plots/model_re_run.png", width = 20, height = 8, scale = 1)
```

## Absolute difference

```{r}
p_comp_data_abs_run <- comp_data_run %>%
  group_by(id,source,tier, run)%>%
  summarise(count = n(),
            duration = sum(duration))%>%
  gather(type, value, -id, -source, -tier,-run)%>%
  spread(run, value)%>%
  mutate(diff = run1 - run2)

 
ggplot(p_comp_data_abs_run, aes(x = id, y = diff, col = tier))+
  geom_segment(aes(x = id, y = 0, xend = id, yend = diff), alpha = .5, col = "black")+
  geom_hline(yintercept = 0, lty = 2, alpha = .5)+
  geom_point(alpha = .5)+
  ylab("Run1 - Run2")+
  facet_grid(tier ~type )+
  theme_minimal()+
  guides(x =  guide_axis(angle = 90))+
  scale_color_ptol()
  

ggsave("./plots/audio_video_diff_run.png", width = 5, height = 6, scale = 1)
```


# Check storytime 
```{r}
story_time <- read_rttm("../Data/one_shot_data/storytime.rttm")


ggplot(story_time, aes(x = tier, ymin = start/60, ymax = end/60, col = tier))+
  geom_linerange(position = position_dodge(width = 0.9), size = 4)+
  coord_flip()+
  #geom_segment(aes(x = start, y = tier, xend = end, yend = tier), size = 5, position = posi)+
  theme_minimal()+
  #ylim(0,100)+
  scale_color_ptol()

story_time %>%
  mutate(start =seconds_to_period(start),
         end = seconds_to_period(end))%>%
  filter( tier == "FEM")
  
  
```
# Audio video comparison outdoor


```{r}
files <- list.files(path = "../Data/outdoor_test/",pattern = "all.rttm", recursive = TRUE)

raw_out_data <- data_frame()
for (f in files) {
  jd <- read_rttm(paste("../Data/outdoor_test/",f,sep=""))
  source <- str_sub(f,-14,-10)
  id <- str_sub(f,14,19)
  data <- jd %>% mutate(id = id, source = source)
  raw_out_data <- bind_rows(raw_out_data, data)
}


out_data <- raw_out_data %>%
  group_by(source)%>%
  summarise(length = max(end),
            stop = min(length))%>%
  right_join(raw_out_data)%>%
  filter(end < 580)

```


```{r}
ggplot(out_data, aes(x = tier, ymin = start/60, ymax = end/60, col = source))+
  geom_linerange(position = position_dodge(width = 0.9), size = 4)+
  coord_flip()+
  #geom_segment(aes(x = start, y = tier, xend = end, yend = tier), size = 5, position = posi)+
  theme_minimal()+
  #ylim(0,100)+
  scale_color_ptol()
  
  
```
```{r}
p_out_data <- out_data %>%
  group_by(source,tier)%>%
  summarise(count = n(),
            duration = sum(duration))%>%
  gather(type, value, -source, -tier)%>%
  spread(source, value)%>%
  mutate(diff = Audio - Video)

 
ggplot(p_out_data, aes(x = tier, y = diff, col = tier))+
  geom_segment(aes(x = tier, y = 0, xend = tier, yend = diff), alpha = .5, col = "black")+
  geom_hline(yintercept = 0, lty = 2, alpha = .5)+
  geom_point(alpha = .5)+
  ylab("Audio - Video")+
  ggtitle("144kHZ")+
  #geom_histogram(stat = "identity",alpha = .5)+
  facet_grid(type~. )+
  theme_minimal()+
  guides(x =  guide_axis(angle = 90))+
  scale_color_ptol()
```

